Automated Reasoning of Relational properties using \\ Abstact Conflict Driven Clause Learning

### 2016-09-01 paper.tex
structure created

\usepackage{import}
\usepackage{times}
\usepackage{graphicx}
\usepackage{cite}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{mathptm}
\usepackage{rotating}
\usepackage{color}
\usepackage{listings}
\usepackage{verbatim}
\usepackage{comment}
\usepackage{alltt}
\usepackage{graphicx}
\usepackage{psfrag}
\usepackage{epsfig}
\usepackage{wasysym} 
\usepackage{subfigure}
\usepackage{paralist}
\usepackage{mdwlist}
\usepackage{multirow}
\usepackage{dingbat}
% \usepackage{hyperref}
\usepackage{colortbl}
\usepackage{booktabs}
\usepackage[algo2e,linesnumbered,ruled,lined]{algorithm2e}
\usepackage{hyperref}
\usepackage{dcolumn}
%\newcolumntype{"}{@{\hskip\tabcolsep\vrule width 1pt\hskip\tabcolsep}}
\makeatother

@@

\title{Equipping Abstact Conflict Driven Clause Learning \\ Solver with Relational Domains}
\maketitle
\begin{abstract}
%
{\em Abstract Conflict Driven Clause Learning} (ACDCL) is a novel program analysis that embeds an 
abstract domain inside the Conflict Driven Clause Learning (CDCL) algorithm. From decision procedure 
perspective, ACDCL is a SAT solver for program analysis constraints and is a strict generalisation of 
propositional CDCL solvers. From Abstract Interpretation point of view, ACDCL can be viewed as an 
abstract interpreter that uses decision and learning to increase the precision of abstract transformers. 
In this paper, we present a technique to generalize ACDCL solvers to reason about relational properties 
of a program using richer abstract domains.  Experimental evidence shows significantly less number of 
decisions and learning iterations compared to propositional SAT solvers -- thereby emphasizing the need
for abstract reasoning using ACDCL.

%
\end{abstract}

@@

\section{Abstract Conflict Driven Clause Learning}
\begin{algorithm2e}[t]
\DontPrintSemicolon
\SetKwFunction{decide}{Decide}
\SetKwFunction{deduce}{deduce}
\SetKwFunction{backtrack}{backtrack}
\SetKwFunction{print}{print}
\SetKwFunction{return}{return}
\SetKwFunction{nondet}{nondet}
\SetKwFunction{run}{run}
\SetKwFunction{learn}{learn}
\SetKwFunction{continue}{continue}
\SetKwFunction{assign}{assign}
\SetKwRepeat{Do}{do}{while}
%\SetKwFunction{assume}{assume}
%\SetKwFunction{isf}{isFeasible}
\SetKwData{safe}{safe}
\SetKwData{unsafe}{unsafe}
\SetKwData{unknown}{unknown}
\SetKwData{true}{true}
\SetKwInOut{Input}{input}
\SetKwInOut{Output}{output}
\SetKw{KwNot}{not}
\begin{small}
\Input{Program $\mathcal{P}$ with properties specified with $assert(c)$}
\Output{The status (\safe or \unsafe) and a counterexample if \unsafe}
\assign result=\deduce(P)\;
\uIf{$result == \perp$} {
  \return \safe \;
}
\uElse
{
  \uIf{is\_gamma\_complete()} {
    \return \unsafe \;
  }
}
\While{$true$} 
{
  \assign decision\_variable = decision\_heuristics($P$)\;
  %\assign decision\_container = decision\_container $\cup$ decision\_variable\; 
  \uIf{decision\_variable == NULL}
  {
    return \unknown\; 
  }
  \uElse
  {
    \assign result=\deduce(P)\;
    \uIf{result == UNKNOWN}
    {
      \uIf{is\_gamma\_complete()} {
        \return \unsafe \;
      }
      \uElse 
      {
        \continue\;
      }
    }
    \uElse
    {
      \Do{$result == \perp$} {
        \uIf{$\neg$ conflict\_analysis()} {
          return \safe \;  
        }
        \assign result=\deduce(P)\;
      }
    }
  }
}
\end{small}
\caption{Abstract Conflict Driven Clause Learning\label{Alg:acdcl}}
\end{algorithm2e}
%
Static program analysis based on abstract
interpretation~\cite{DBLP:conf/emsoft/Cousot07} has been widely used to
verify certain classes of properties for safety-critical systems.  In
abstract interpretation, a given program is analysed with respect to a set
of given abstract domains.  However, ACDCL is a novel program analysis 
technique that embeds an abstract domain inside the CDCL algorithm.
From the abstract interpretation point of view, ACDCL is an abstract 
interpreter that uses decision and learning to increase transformer precision. 
From the decision procedure perspective, ACDCL is a SAT solver for program 
analysis constraints and is thus a strict generalisation of propositional CDCL solvers.
Constraint propagation in ACDCL uses fixed point iteration, decisions restrict the 
range of intervals and learning generates program analysis constraints (not assumptions) 
that preserve the error reachability.  Moreover, ACDCL implicitly 
perform program and property driven trace partitioning to increase the precision
of the analysis.  We observe that the abstract domains necessary for 
hardware property checking are -- booleans, constants, interval, equality 
and octagons domains.

@@

>>>>

\usepackage{import}
\usepackage{times}
\usepackage{graphicx}
\usepackage{cite}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{mathptm}
%\usepackage{rotating}
\usepackage{color}
\usepackage{listings}
\usepackage{verbatim}
\usepackage{comment}
\usepackage{alltt}
\usepackage{graphicx}
\usepackage{psfrag}
\usepackage{epsfig}
\usepackage{wasysym} 
\usepackage{subfigure}
\usepackage{paralist}
%\usepackage{mdwlist}
%\usepackage{multirow}
\usepackage{dingbat}
% \usepackage{hyperref}
%\usepackage{colortbl}
%\usepackage{booktabs}
\usepackage[algo2e,linesnumbered,ruled,lined]{algorithm2e}
\usepackage{hyperref}
%\usepackage{dcolumn}
%\newcolumntype{"}{@{\hskip\tabcolsep\vrule width 1pt\hskip\tabcolsep}}
\makeatother

@@

%\title{Equipping Abstact Conflict Driven Clause Learning \\ Solver with Relational Domains}
\title{Automated Reasoning of Relational properties using \\
Abstact Conflict Driven Clause Learning}
\maketitle
\begin{abstract}
%
{\em Abstract Conflict Driven Clause Learning} (ACDCL) is a novel program analysis that embeds an 
abstract domain inside the Conflict Driven Clause Learning (CDCL) algorithm. From decision procedure 
perspective, ACDCL is a SAT solver for program analysis constraints and is a strict generalisation of 
propositional CDCL solvers. From Abstract Interpretation point of view, ACDCL can be viewed as an 
abstract interpreter that uses decision and learning to increase the precision of abstract transformers. 
In this paper, we present a technique to generalize ACDCL solvers to reason about relational properties 
of a program by embedding relational domains like octagon domain inside the ACDCL solver.  Experimental 
evidence shows significantly less number of decisions and learning iterations required by ACDCL solver to 
prove programs with relational properties compared to bit-blasting and applying propositional SAT solvers -- 
thereby emphasizing the need for abstract reasoning using ACDCL. 
%
\end{abstract}

@@

\section{Abstract Conflict Driven Clause Learning}
\begin{algorithm2e}[t]
\DontPrintSemicolon
\SetKwFunction{decide}{Decide}
\SetKwFunction{deduce}{deduce}
\SetKwFunction{backtrack}{backtrack}
\SetKwFunction{print}{print}
\SetKwFunction{return}{return}
\SetKwFunction{nondet}{nondet}
\SetKwFunction{run}{run}
\SetKwFunction{learn}{learn}
\SetKwFunction{continue}{continue}
\SetKwFunction{assign}{assign}
\SetKwRepeat{Do}{do}{while}
%\SetKwFunction{assume}{assume}
%\SetKwFunction{isf}{isFeasible}
\SetKwData{safe}{safe}
\SetKwData{unsafe}{unsafe}
\SetKwData{unknown}{unknown}
\SetKwData{true}{true}
\SetKwInOut{Input}{input}
\SetKwInOut{Output}{output}
\SetKw{KwNot}{not}
\begin{small}
\Input{Program $\mathcal{P}$ with properties specified with $assert(c)$}
\Output{The status (\safe or \unsafe) and a counterexample if \unsafe}
\assign result=\deduce(P)\;
\uIf{$result == \perp$} {
  \return \safe \;
}
\uElse
{
  \uIf{is\_gamma\_complete()} {
    \return \unsafe \;
  }
}
\While{$true$} 
{
  \assign decision\_variable = decision\_heuristics($P$)\;
  %\assign decision\_container = decision\_container $\cup$ decision\_variable\; 
  \uIf{decision\_variable == NULL}
  {
    return \unknown\; 
  }
  \uElse
  {
    \assign result=\deduce(P)\;
    \uIf{result == UNKNOWN}
    {
      \uIf{is\_gamma\_complete()} {
        \return \unsafe \;
      }
      \uElse 
      {
        \continue\;
      }
    }
    \uElse
    {
      \Do{$result == \perp$} {
        \uIf{$\neg$ conflict\_analysis()} {
          return \safe \;  
        }
        \assign result=\deduce(P)\;
      }
    }
  }
}
\end{small}
\caption{Abstract Conflict Driven Clause Learning\label{Alg:acdcl}}
\end{algorithm2e}
%
Static program analysis based on abstract
interpretation~\cite{DBLP:conf/emsoft/Cousot07} has been widely used to
verify certain classes of properties for safety-critical systems.  In
abstract interpretation, a given program is analysed with respect to a set
of given abstract domains.  However, ACDCL is a novel program analysis 
technique that embeds an abstract domain inside the CDCL algorithm.
From the abstract interpretation point of view, ACDCL is an abstract 
interpreter that uses decision and learning to increase transformer precision. 
From the decision procedure perspective, ACDCL is a SAT solver for program 
analysis constraints and is thus a strict generalisation of propositional CDCL solvers.
Constraint propagation in ACDCL uses fixed point iteration, decisions restrict the 
range of intervals and learning generates program analysis constraints (not assumptions) 
that preserve the error reachability.  Moreover, ACDCL implicitly 
perform program and property driven trace partitioning to increase the precision
of the analysis.  
\Omit{
We observe that the abstract domains necessary for 
hardware property checking are -- booleans, constants, interval, equality 
and octagons domains.
}

@@

\section{Deduction Phase}
Overapproximating.
\subsection{Forward analysis with strongest post-condition}
\subsection{Chaotic iteration strategy} 
\section{Decision Heuristics}
Berkmin, longest-range, random, ordered, octagons 
\section{Abstract Domains}
Support for Interval, Octagons
\section{Clause Learning}
1.DPLL style -- chronological backtracking \\
2. CDCL style -- non-chronological backtracking \\
  a. first-uip \\
  b. last-uip \\
